Determinism, Complexity, and Predictability in Computer Performance

### 2014-04-12 wpe.tex
typo in wpe

As a final note: there has been prior work under a similar title to
ours~\cite{haven2005}, but there are only superficial similarities
between the two research projects.  Haven {\sl et al.} utilize the
relative entropy to quantify how much better one can predict the exact
state of a system from a distribution over system states evolved from 
a small ensemble around a prior known exact state, verses its asymptotic
distribution, requiring a model to perform the evolution. Our work
quantifies the predictability of a single observed time series using
weighted permutation entropy and makes no assumptions about the
underlying dynamics.

>>>>

As a final note: there has been prior work under a similar title to
ours~\cite{haven2005}, but there are only superficial similarities
between the two research projects.  Haven {\sl et al.} utilize the
relative entropy to quantify how much better one can predict the exact
state of a system from a distribution over system states evolved from 
a small ensemble around a prior known exact state, versus its asymptotic
distribution, requiring a model to perform the evolution. Our work
quantifies the predictability of a single observed time series using
weighted permutation entropy and makes no assumptions about the
underlying dynamics.
